Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-15 doc/paper-lcr.tex
added framework

\section{Halo Model and Mass distribution}
\label{sec:model}

@@

% PJM: What is this defeatism?!
% it is nearly impossible to know the true $\kappax$ for a
% line of sight, and without a knowledge of $\kappax^{\mathrm{true}}$ it is hard to
% quantify if there is a bias induced by using different $\kappax$ estimators.
%
% A source with known unlensed brightness e.g. a strongly lensed type Ia
% Supernova \flag{cite some SNe papers} or a source of known unlensed size \flag{ideas?}
% would break the mass-sheet degeneracy and provide a value for $\kappax$, but
% \flag{no?} such systems are currently known.

Cosmological dark matter simulations can be used to generate mock lines of
sight and can be raytraced through to give each mock sightline a $\kappax$ value...
\todo{Stefan}{Write section on how the ray tracing was done and how halos are extracted from
 the MS n-body particles}

Transforming the photometometric galaxy catalogue into a  catalogue of
halo masses, positions, and redshifts, will enable us to attempt a
reconstruction of the convergence induced by every halo near a line of sight.
This is the subject of the first subsection below. We also need to account for
the mass in the Universe that is not associated with the galaxies we can see
-- this is the subject of the second subsection below.

@@

\subsection{Halos}

@@

\section{Tests with known halo mass and redshift}
\label{sec:knownMh+z}

@@

\section{Tests on mock catalogs}
\label{sec:obsMstar+z}

@@

\subsection{Reconstructions of Smaller and Shallower Fields}

@@

%\subsection{Reconstructing Biased Lines of Sight}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\comments{
\section{Time Delay Distances}
\label{sec:Dt}

Folding the kappa uncertainties into time delay distance uncertainties. Toy
model: same zl and zs, allows simple product of pdfs to obtain estimate of P(D).

Make mock sample of lenses, all wit B1608 zd and zs, but with different kappas.
Draw kappas from Stefan's *lens* distribution. Can we correct for the selection
effect?

@@

\subsection{The Impact of Selection Effects}
\label{sec:Dt:selection}

\phil{How does distance accuracy vary with:}
\begin{itemize}
\item Depth of catalog? mlim = 22, 24, 26?
\item Overdensity cuts? Remove underdense fields, overdense fields (from
reconstructed kappa)
\item Shear-sensitive selection? What if we only selected quads?
\end{itemize}

@@

\phil{How does distance accuracy improve with:}
\begin{itemize}
\item Spectroscopic coverage? For galaxies above some mlim? For targets with
high kappa contribution (based on photometry)?
\item IR coverage for all objects? Improves photo-z and Mstar.
\item Including shear information from lens model? Assume accurate but
uncertain extertanl shear.
\end{itemize}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{figure}
% \centering\includegraphics[width=0.99\linewidth]{figs/something.png}
% \caption{An example figure.}
% \label{fig:sizemass}
% \end{figure}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Estimating external convergence: The halo model approximation}
\label{sec:model}

@@

% A source with known unlensed brightness e.g. a strongly lensed type Ia
% Supernova \flag{cite some SNe papers} or a source of known unlensed size \flag{ideas?}
% would break the mass-sheet degeneracy and provide a value for $\kappax$, but
% \flag{no?} such systems are currently known.

\subsection{Ray-tracing through simulated Lines of Sight}
\label{subsec:raytracing}
Cosmological dark matter simulations can be used to generate mock lines of
sight and can be raytraced through to give each mock sightline a $\kappax$ value...
\todo{Stefan}{Write section on how the ray tracing was done}

\subsection{Generating mock lightcones from simulations}

\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}

Transforming the photometometric galaxy catalogue into a  catalogue of
halo masses, positions, and redshifts, will enable us to attempt a
reconstruction of the convergence induced by every halo near a line of sight.
This is the subject of \ref{subsec:halos}. We also need to account for
the mass in the Universe that is not associated with the galaxies we can see
-- this is the subject of \ref{subsec:voids}.

@@

\subsection{Halos}
\label{subsec:halos}

@@

\section{Testing the halo model approximation with known halo mass and redshift}
\label{sec:knownMh+z}

\subsection{How does $\kappah$ relate to $\kappax$?}

\subsection{Does converting from $\kappah$ to $\kappax$ work?}

\subsection{Where does $\kappah$ come from?}
\subsubsection{Magnitude}
\subsubsection{Distance}
\subsubsection{Redshift}

@@

\section{Applying the Halo Model approximation to mock catalogs}
\label{sec:obsMstar+z}

@@

%\subsection{Reconstructions of Smaller and Shallower Fields}

@@

\section{Testing for Systematic errors}
\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
\subsection{Selecting bias from a subset of lines of sight?}
\subsubsection{Selecting only the lines of sight with tight $\pr(\kappax)$}
\subsubsection{Selecting only high shear lines of sight}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\comments{

@@

@@

\phil{How does distance accuracy improve with:}
\begin{itemize}
\item Spectroscopic coverage? For galaxies above some mlim? For targets with
high kappa contribution (based on photometry)?
\item IR coverage for all objects? Improves photo-z and Mstar.
\item Including shear information from lens model? Assume accurate but
uncertain extertanl shear.
\end{itemize}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
